Partitioned Local Depth (PaLD) Community Cluster Analyses in R

### 2022-06-02 r-journal/dagostino-mcgowan.Rmd
add cultures data

In addition, the package provides a number of pertinent example data sets commonly used to demonstrate cluster algorithms, including a synthetic data set of two-dimensional points created by \citet{gionis1clustering} to demonstrate clustering aggregation, clustering data generated from the scikit-learn Python package \citep{pedregosa2011scikit}, data describing cognate relationships between words across 87 Indo-European languages \citep{dyen92}, data compiled by \cite{tissue} of tissue gene expressions, and three example data sets generated for the \citet{berenhaut2022social} paper.

>>>>

In addition, the package provides a number of pertinent example data sets commonly used to demonstrate cluster algorithms, including a synthetic data set of two-dimensional points created by \citet{gionis1clustering} to demonstrate clustering aggregation, clustering data generated from the scikit-learn Python package \citep{pedregosa2011scikit}, data describing cognate relationships between words across 87 Indo-European languages \citep{dyen92}, data compiled by \cite{tissue} of tissue gene expressions, data from the World Values Survey \citep{inglehart2014world} on cultural values regarding family, religion, education, and institutions for several regions \citep{muthukrishna2020beyond}, and three example data sets generated for the \citet{berenhaut2022social} paper.

### 2022-06-02 r-journal/dagostino-mcgowan.tex
add cultures data

\begin{Schunk}
\begin{Sinput}
graphs <- community_graphs(cohesion)
graphs[["G_strong"]]
\end{Sinput}
\begin{Soutput}
#> IGRAPH b2835f9 UNW- 6 3 -- 
#> + attr: name (v/c), weight (e/n)
#> + edges from b2835f9 (vertex names):
#> [1] A--B A--E D--F
\end{Soutput}
\end{Schunk}

@@

\begin{Schunk}
\begin{Sinput}
french_neighbors <- igraph::neighbors(cognate_graph_strong, "French")
french_neighbors
\end{Sinput}
\begin{Soutput}
#> + 8/87 vertices, named, from e40f165:
#> [1] Italian         Ladin           Provencal       Walloon        
#> [5] French_Creole_C French_Creole_D Spanish         Catalan
\end{Soutput}
\end{Schunk}

>>>>

\begin{Schunk}
\begin{Sinput}
graphs <- community_graphs(cohesion)
graphs[["G_strong"]]
\end{Sinput}
\begin{Soutput}
#> IGRAPH 4190215 UNW- 6 3 -- 
#> + attr: name (v/c), weight (e/n)
#> + edges from 4190215 (vertex names):
#> [1] A--B A--E D--F
\end{Soutput}
\end{Schunk}

@@

\begin{Schunk}
\begin{Sinput}
french_neighbors <- igraph::neighbors(cognate_graph_strong, "French")
french_neighbors
\end{Sinput}
\begin{Soutput}
#> + 8/87 vertices, named, from 4db266d:
#> [1] Italian         Ladin           Provencal       Walloon        
#> [5] French_Creole_C French_Creole_D Spanish         Catalan
\end{Soutput}
\end{Schunk}
